\documentclass{beamer}

\usetheme{metropolis}

% --- Ripe tomato red ---}
\definecolor{mTomato}{HTML}{B82F17}

% Disable Metropolis' automatic tinting everywhere
\setbeamercolor{normal text}{fg=black,bg=white}

% Frametitle
\setbeamercolor{frametitle}{bg=mTomato, fg=white}

% Progress bar
\setbeamercolor{progress bar}{fg=mTomato, bg=mTomato}

% Title separator
\setbeamercolor{title separator}{fg=mTomato}

% Alerts
\setbeamercolor{alerted text}{fg=mTomato}

% Section pages
\setbeamercolor{section title}{fg=white, bg=mTomato}

% Palette (top bar on title slide)
\setbeamercolor{palette primary}{bg=mTomato, fg=white}

\newcommand{\given}{\,|\,}

\title{Information Theory}
\author{Brendon J. Brewer}
%\date{\today}

\begin{document}

\maketitle

\begin{frame}{Why Information Theory?}
If you take the log of a probability, you will appear to understand
profound truths.

\end{frame}


\begin{frame}{Why Information Theory?}
``But you remember this. When you control the mail, you control... information.''
--- Newman
\end{frame}


\begin{frame}{Probability Theory}
Information theory is built upon probability theory, like an extra `layer'
that is automatically present whenever you use probabilities.
In the first week, we will spend some time revising probability theory.
\end{frame}


\begin{frame}{Probability Theory: Sum and Product Rules}
The sum rule of probabilities is
\begin{align}
P(A \vee B \given C) &= P(A \given C) + P(B \given C) - P(A, B \given C).
\end{align}

\pause

Here, $A$, $B$, and $C$ are any three statements or propositions.
The vertical bar means `given'. The $\vee$ means `logical OR'.
The comma means `logical AND'.

\pause

Throughout the equation, $C$ is the background context.

\end{frame}



\begin{frame}{Probability Theory: Sum and Product Rules}
The product rule of probabilities is
\begin{align}
P(A, B \given C) &= P(A \given C)P(B \given A, C).
\end{align}

\pause

You might be used to calling $A$, $B$ and $C$ {\em events}, defined as subsets
of the {\em sample space}. The logical OR becomes set union $\cup$,
and the logical AND becomes set intersection $\cap$. You are welcome to use
that terminology and notation, but it is not my preference.

\end{frame}


\begin{frame}{Probability Theory: Sum and Product Rules}
If $A$ and $B$ are mutually exclusive (given $C$), the sum rule simplifies
to
\begin{align}
P(A \vee B \given C) &= P(A \given C) + P(B \given C).
\end{align}

\pause

If $A$ and $B$ are independent (given $C$), the product rule simplifies to

\begin{align}
P(A, B \given C) &= P(A \given C)P(B \given C).
\end{align}


\end{frame}



\begin{frame}{Exercise: }
If $A$ and $B$ are mutually exclusive (given $C$), the sum rule simplifies
to
\begin{align}
P(A \vee B \given C) &= P(A \given C) + P(B \given C).
\end{align}

\pause

If $A$ and $B$ are independent (given $C$), the product rule simplifies to

\begin{align}
P(A, B \given C) &= P(A \given C)P(B \given C).
\end{align}


\end{frame}


\end{document}

